### 2014-03-08 src/results.Rnw
update

\section{Results}
\label{sec:results}
We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
The number of mutators in RND is
 Sexpr{sum(m.lrnd.pit.mutation.total) / sum(m.sdl.pit.mutation.total)} times SDL.

The total mutants for all is Sexpr{sum(m.pit.mutation.total)}, for rnd is Sexpr{sum(m.lrnd.pit.mutation.total)} and for sdl is Sexpr{sum(m.sdl.pit.mutation.total)}

>>>>

\section{Results}
\label{sec:results}
Our analysis of results suggests that different kinds of operator selection criterias can actually provide better reduction in mutants while not reducing the approximatin accuracy below acceptable limits.
